A Temporal Logic Based Framework for Intrusion Detection

### 2023-09-06 Paper/main.tex
update

>>>>

\textbf{Multi-domain Buffer Overflows}
According to~\cite{piromsopa2006buffer}, a buffer-overflow attack is an attack that (possibly implicitly) uses memory-manipulating operations to overflow a buffer which results in the modification of an address to point to malicious or unexpected code. In this case, we will integrate data from various log sources; to be more exact, we will examine both network and web server access logs to determine when a server buffer overflow attack has been performed. We search through network packets for binary data; then web server's access logs are examined to see if a corresponding event, in which the web server correctly terminates the connection after receiving some binary data, can be located. If no matching log record is discovered within a predetermined timeout, it means that the buffer overflow attack was successful. The following formula captures this scenario:
